PM Mungbean meta-analysis

### 2021-01-20 02_Preliminary_analysis.Rmd
move save table to docx to it's own chunk

```{r Full_Trial_Summary_table, warning= FALSE}
Sev_yield_table <-
PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(n = n(),
             m_PM_sev_control = round(mean(PM_sev_control, na.rm = TRUE),digits = 2),
             min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE),digits = 2),
             max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE),digits = 2),
             m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE),digits = 3),
             min_PM_yield = round(min(PM_y_treat, na.rm = TRUE),digits = 3),
             max_PM_yield = round(max(PM_y_treat, na.rm = TRUE),digits = 3),
             .groups = "drop")%>%
   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
   arrange(year)%>%
   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - "))%>%
   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - "))%>%
   select(-c(min_PM_sev,max_PM_sev,min_PM_yield,max_PM_yield)) %>%
   flextable() %>%
   set_header_labels(trial_ref = "Trial code",
                     location = "Location",
                     year = "Year",
                     planting_date = "Sowing date",
                     first_sign_disease = "PM onset",
                     n = "n",
                     m_PM_sev_control = "Control mean\nPM severity",
                     PM_sev_range = "PM severity\nrange*",
                     m_PM_yield_control = "Control\nmean yield",
                     yield_range = "Yield range\n(t / ha)*"
                     ) %>%
   fontsize(size = 8,part = "body")%>%
   fontsize(size = 10, part = "header")%>%
   align(j = 3:10, align = "center", part = "all") %>%
   autofit() %>%
   width(j = 7:10, width = 0.9)%>%
   width(j = 3, width = 0.5)%>%
   set_caption("Table 1: Mean yield and severity for trials included in the meta-analysis. Powdery mildew (PM) onset, number of treatments per trial (n), PM mean plot severity of the non-fungicide treated plots and the severity range in fungicide treatments; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare")
Sev_yield_table

doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = Sev_yield_table)
doc <- officer::body_end_section_landscape(doc)
print(doc, target = "paper/figures/Table1_severity&yield.docx")

>>>>

```{r Full_Trial_Summary_table, warning= FALSE}
Sev_yield_table <-
PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(n = n(),
             m_PM_sev_control = round(mean(PM_sev_control, na.rm = TRUE),digits = 2),
             min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE),digits = 2),
             max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE),digits = 2),
             m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE),digits = 3),
             min_PM_yield = round(min(PM_y_treat, na.rm = TRUE),digits = 3),
             max_PM_yield = round(max(PM_y_treat, na.rm = TRUE),digits = 3),
             .groups = "drop")%>%
   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
   arrange(year)%>%
   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - "))%>%
   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - "))%>%
   select(-c(min_PM_sev,max_PM_sev,min_PM_yield,max_PM_yield)) %>%
   flextable() %>%
   set_header_labels(trial_ref = "Trial code",
                     location = "Location",
                     year = "Year",
                     planting_date = "Sowing date",
                     first_sign_disease = "PM onset",
                     n = "n",
                     m_PM_sev_control = "Control mean\nPM severity",
                     PM_sev_range = "PM severity\nrange*",
                     m_PM_yield_control = "Control\nmean yield",
                     yield_range = "Yield range\n(t / ha)*"
                     ) %>%
   fontsize(size = 8,part = "body")%>%
   fontsize(size = 10, part = "header")%>%
   align(j = 3:10, align = "center", part = "all") %>%
   autofit() %>%
   width(j = 7:10, width = 0.9)%>%
   width(j = 3, width = 0.5)%>%
   set_caption("Table 1: Mean yield and severity for trials included in the meta-analysis. Powdery mildew (PM) onset, number of treatments per trial (n), PM mean plot severity of the non-fungicide treated plots and the severity range in fungicide treatments; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare")
Sev_yield_table
```

```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = Sev_yield_table)
doc <- officer::body_end_section_landscape(doc)
print(doc, target = "paper/figures/Table1_severity&yield.docx")
